String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-08-30 2023-1-19/sections/overview.tex
overview

Specifically, to reduce the sizes of $\cB$, we take $\vec{0}$-labeled transitions as $\epsilon$-transitions, determinize $\cB$, and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), resulting in a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b).
Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
%The evaluation in Table~\ref{tab:results_simp} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.

>>>>

Specifically, to reduce the sizes of $\cB$, we determinize $\cB$, and apply the minimization algorithm to the resulting deterministic finite automaton (DFA), resulting in a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b). 
Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. Furthermore, if $\cB$ contains $\vec{0}$-labeled transitions, then we can take these transitions as $\epsilon$-transitions and potentially reduce the sizes of automata further. 
%The evaluation in Table~\ref{tab:results_simp} shows that we can solve 1503 more instances after utilizing simplification techniques, with \%54.8 less average time.
